### 2018-01-29 includes/abstract.tex
starting pass with abstract. All changes are suggestions.

\begin{abstract}

    In this paper, we introduce \fuzzer{}: a modular \smt{} problem transformer and generator for string solvers. We supply a repository of problems generated by \fuzzer{} in \smtfull{} format. We systemically compare \theSolvers{} on groups of such problems focusing on different combinations of string operators, and identify problems that are particularly challenging for some solvers. We briefly explain our observations and showcase how \fuzzer{} helped identify causes of the performance degradations in \us{}.

\end{abstract}

>>>>

\begin{abstract}
    Performant SMT solvers rely on powerful heuristics and highly optimized implementations
    that need to be validated and tested. 
    To do this researchers often depend 
    on tedious to produce hand-crafted benchmarks, and hard to procure industrial suites.
    In this paper we offer an alternative to string \smt{} solver developers: 
    \fuzzer{}, a modular problem transformer and generator.
    We showcase \fuzzer{} by producing a repository of \smtfull{} format problems;
    systemically comparing \theSolvers{} on these problems; and 
    identifying causes of performance degradations in \us{}.
\end{abstract}
